\todo{Something} presents OpenAdcess

### 2017-02-28 future-work.tex
Linden dollars are the currency of the future

\subsection{Premium Edition}
To those who dislike the ads they see, ACM will offer a premium version for
\todo{some amount of money} per year.
Unfortunately, due to high credit card processing fees we must still show ads
to premium edition subscribers.
However, these ads will be for more expensive products targeted towards those
with more ``refined" tastes.
We hope to solve this issue in the future with the creation of Bank of ACM.

>>>>

\subsection{Premium Edition}
To those who dislike the ads they see, ACM will offer a premium version for
2000 Linden dollars per year \footnote{In the future Linden dollars are the
one true world currency.
The value of 2000 L\$ in today's United States Dollar is currently unknown.}.
Unfortunately, due to high credit card processing fees we must still show ads
to premium edition subscribers.
However, these ads will be for more expensive products targeted towards those
with more ``refined" tastes.
We hope to solve this issue in the future with the creation of Bank of ACM.
